---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gitgantt

<!-- badges: start -->
<!-- badges: end -->

The goal of gitgantt is to make it easier to create project plans via GitHub.

Problem: you need to show your plan in a report or funding application, but all the planned work is stashed in GitHub issues.

Solution: add lines containing `GanttStart: ` and `GanttDue: ` to your issues and use **gitgantt** to convert them into an attractive Gantt chart in a single line of code!

```{r example}
library(gitgantt)
gg_timevis(owner = "ATFutures", repo = "who3")
```

## Installation

<!-- You can install the released version of gitgantt from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("gitgantt") -->
<!-- ``` -->

Install the development version from [GitHub](https://github.com/) with:

``` r
remotes::install_github("robinlovelace/gitgantt")
```

## How it works

The packages uses [`gh`]() to extract issue data from GitHub and code inspired by [jennybc/analyze-github-stuff-with-r](https://github.com/jennybc/analyze-github-stuff-with-r) to clean the data into a `tibble`:

```{r}
issue_list = gg_issue_list(owner = "ATFutures", repo = "who3")
issue_df = gg_issue_df(issue_list)
issue_df
```

## Thanks

This project is inspired by and builds on:

- Excellent demonstration of using `gh` in the [analyze-github-stuff-with-r](https://github.com/jennybc/analyze-github-stuff-with-r) by Jenny Bryan
- The [GanttLab](https://www.ganttlab.org/) project, which initially inspired this effort and defined the `GanttStart: ` convention
- The [`gh-issues-gantt`](https://github.com/neyric/gh-issues-gantt) JavaScript package, which in turn builds on [jQuery.Gantt](http://taitems.github.com/jQuery.Gantt/) (raising the possibility for using this for the visualisation)
- The [`gh`](https://github.com/r-lib/gh) R package, an interface GitHub's API
